Generality in food webs scales with species richness, not latitude

### 2015-04-10 manuscript/latitudepaper.tex
Added last round of corrections before sending off to T

  We then assessed the impact of latitude on the scaling relationships between $Z$, $G$, $V$, and $S$. 
  [[If the species-rich tropics truly have narrower 
  niches~\citep{Brown2004}, then we would expect to see less increase in mean numbers of links, 
  predators, and prey with increasing species richness in the tropics. ]]
  In the context of the scaling relationships above, note that this implies that we aim to determine the effect of latitude on
  the scaling exponent $\beta$. As when examining the relationships between latitude and each food 
  web property directly, we included a categorical variable for ecosystem type (stream, lake, 
  terrestrial, marine, or estuary), as well as interactions between food web type and latitude.

@@

  For each property in $Z$, $G$, and $V$, we used the form of the equation that was best supported
  when describing the scaling of the property with species richness alone~\citep{Xiao2011}.
  We then simplified each model following the same procedure as for the relationships between
  latitude and food-web properties, except that $S$ was retained in all reduced models.

@@

  We were also interested in the ways that scaling relationships with $S$ might
  be affected by changes to the distribution of species among trophic levels. To
  that end, we repeated all of the above analyses replacing species richness by
  proportion of basal resources $B$, proportion of intermediate consumers $I$,
  or proportion of top predators $T$. All model fitting and model
  simplification procedures were identical to those described for species
  richness.

@@

  Contrary to the expected latitudinal gradient, the best-fit version of
  equation~(\ref{Latfull}) for species richness did not include a signficant effect of latitude for any ecosystem type except streams
  ($\beta_{Latitude}$=0.095, $p$=0.626; $\beta_{Latitude:Stream}$=-1.69, $p$=0.007).  This
  relationship was robust to the removal of three outliers (based on Cook's Distance). In the best-fit versions of
  equation~(\ref{Latfull}) for link density and vulnerability, there were once again
  significant relationships with latitude in stream food webs but 
  no other ecosystem type 
  ($\beta_{Latitude}$=0.022, $p$=0.592 and $\beta_{Latitude:Stream}$=-0.356, $p$=0.007 for link density; 
  $\beta_{Latitude}$=0.011, $p$=0.589 and $\beta_{Latitude:Stream}$=-0.179, $p$=0.007 for vulnerability). However, after
  the removal of three outliers these relationships were no longer
  significant. The best-fit
  version of equation~(\ref{Latfull}) for generality did not include any effect of
  latitude in any ecosystem type.

@@

  When considering the relationships between species richness and proportions 
  of basal resources, intermediate consumers, and top predators and all response variables 
  (link density, generality, vulnerability), equation~(\ref{Loglog}) had a
  lower AIC than did equation~(\ref{Power}). This indicates that the
  data support an assumption of multiplicative lognormal error better than an
  assumption of additive normal error. That is, models where $\epsilon$ is
  modelled as an additive term on
  the logarithmic scale provide a better description of the data than models
  where $\epsilon$ is modelled as an additive term on the arithmetic scale.  
  We therefore used logarithmic-form models when assessing the
  effect of latitude on scaling relationships  with $S$.

@@

Link density, generality, and vulnerability each increased with increasing
species richness (Fig.~\ref{S}; $\beta_0$=0.745, $p$\textless0.001; $\beta_0$=0.675,
$p$\textless0.001; and $\beta_0$=0.745, $p$\textless0.001).  For estuarine,
marine, and terrestrial food webs this increase did not vary with latitude
($\beta_{Latitude}$=-0.001, $p$=0.334; $\beta_{Latitude}$=-0.001, $p$=0.354;
and $\beta_{Latitude}$=-0.001, $p$=0.334). In lake food webs, link density,
generality, and vulnerability all increased more quickly towards the poles
($\beta_{Latitude:Lake}$=0.004, $p$=; $\beta_{Latitude:Lake}$=0.005,
$p$=0.002; and $\beta_{Latitude:Lake}$=0.005, $p$=0.008, respectively) In
stream food webs, only the strength of scaling of generality increased with
latitude ($\beta_{Latitude}$=0.007, $p$=0.002).

In general, link density, generality, and vulnerability decreased as the
proportion of basal resources in a web increased (Fig.~\ref{B}). For
estuarine, lake, and stream food webs these decreases were steeper towards the
poles ($\beta_{Latitude}$=-0.007, $p$=0.006 for link density;
$\beta_{Latitude}$=-0.009, $p$=0.002 for generality; and
$\beta_{Latitude}$=-0.007, $p$=0.006 for vulnerability).
In marine food webs there was very little effect of latitude on
the strength of scaling ($\beta_{Latitude:Marine}$=0.009, $p$=0.047; 
$\beta_{Latitude:Marine}$=0.011, $p$=0.028; 
and $\beta_{Latitude:Marine}$=0.009, $p$=0.047 respectively),
while in terrestrial food webs scaling was stronger towards the 
equator ($\beta_{Latitude:Terrestrial}$=0.013, $p$=0.002; 
$\beta_{Latitude:Terrestrial}$=0.015, $p$=0.001; 
and $\beta_{Latitude:Terrestrial}$=0.013, $p$=0.002).

In contrast to the proportion of basal resources, link density, generality,
and vulnerability tended to increase with increasing proportions of
intermediate consumers (Fig.~\ref{I}). The best-fit models for scaling of link
density and vulnerability with the proportion of intermediate consumers did
not include any effect of latitude on scaling in any ecosystem type. Scaling
of generality was stronger towards the equator in estuarine, lake, marine, and
stream food webs ($\beta_{Latitude}$=-0.006, $p$=0.009) and varied little with
latitude in terrestrial food webs ($\beta_{Latitude:Terrestrial}$=0.008,
$p$=0.053). In lake and stream food webs, generality increased more weakly
with the proporiton of intermediate consumers such that, at low proportions,
the effect of latitude could negate or reverse the increase.

As with the proportion of basal resources, link density, generality, and
vulnerability decreased as the proportion of top predators increased. For
estuarine, lake, and marine food webs scaling of link density, generality, and
vulnerability did not vary significantly with latitude
($\beta_{Latitude}$=-0.001, $p$=0.527 for link density;
$\beta_{Latitude}$=-0.001, $p$=0.526 for vulnerability; the best-fit model for
generality did not include any terms for latitude in any ecosystem type). In
stream and terrestrial food webs, the decrease in link density and
vulnerability was steeper towards the poles, although this trend was
significant only in streams ($\beta_{Latitude:Stream}$=0.015,
$p$\textless0.001 and $\beta_{Latitude:Terrestrial}$=0.006, $p$=0.069 for link
density; $\beta_{Latitude:Stream}$=0.015, $p$\textless0.001 and
$\beta_{Latitude:Terrestrial}$=0.006, $p$=0.067 for vulnerability).

>>>>

  We then assessed the impact of latitude on the scaling relationships between species richness and 
  link density, generality, vulnerability.
  [[If the species-rich tropics truly have narrower 
  niches~\citep{Brown2004}, then we would expect to see less increase in mean numbers of links, 
  predators, and prey with increasing species richness in the tropics. ]]
  In the context of the scaling relationships above, note that this implies that we aim to determine the effect of latitude on
  the scaling exponent $\beta$. As when examining the relationships between latitude and each food 
  web property directly, we included a categorical variable for ecosystem type (stream, lake, 
  terrestrial, marine, or estuary), as well as interactions between food web type and latitude.

@@

  For each property in link density, generality, and vulnerability, we used the form of the equation that was best supported
  when describing the scaling of the property with species richness alone~\citep{Xiao2011}.
  We then simplified each model following the same procedure as for the relationships between
  latitude and food-web properties, except that species richness was retained in all reduced models.

@@

  We were also interested in the ways that scaling relationships with species richness might
  be affected by changes to the distribution of species among trophic levels. To
  that end, we repeated all of the above analyses replacing species richness by
  proportion of basal resources $B$, proportion of intermediate consumers $I$,
  or proportion of top predators $T$. All model fitting and model
  simplification procedures were identical to those described for species
  richness.

@@

  Contrary to the expected latitudinal gradient, the best-fit version of
  equation~(\ref{Latfull}) for species richness did not include a signficant effect of latitude for any ecosystem type except streams
  ($\beta_{Latitude}$=0.095, $p$=0.626; $\beta_{Latitude:Stream}$=-1.69, $p$=0.007).  This
  relationship was robust to the removal of three outliers (based on Cook's Distance). In the best-fit versions of
  equation~(\ref{Latfull}) for link density and vulnerability, there were once again
  significant relationships with latitude in stream food webs, but after the removal of three outliers these trends
  were no longer significant. Link density and vulnerability did not vary with latitude in any other ecosystem type.
  Similarly, the best-fit version of equation~(\ref{Latfull}) for generality did not include any effect of
  latitude in any ecosystem type.

@@

  When considering the relationships between species richness and proportions 
  of basal resources, intermediate consumers, and top predators and all response variables 
  (link density, generality, vulnerability), equation~(\ref{Loglog}) had a
  lower AIC than did equation~(\ref{Power}). This indicates that the
  data support an assumption of multiplicative lognormal error better than an
  assumption of additive normal error. That is, models where $\epsilon$ is
  modelled as an additive term on
  the logarithmic scale provide a better description of the data than models
  where $\epsilon$ is modelled as an additive term on the arithmetic scale.  
  We therefore used logarithmic-form models when assessing the
  effect of latitude on scaling relationships  with species richness.

@@

Link density, generality, and vulnerability each increased with increasing
species richness (Fig.~\ref{S}; $\beta_0$=0.745, $p$\textless0.001; $\beta_0$=0.675,
$p$\textless0.001; and $\beta_0$=0.745, $p$\textless0.001 respectively).  For estuarine,
marine, and terrestrial food webs this increase did not vary with latitude
($\beta_{Latitude}$=-0.001, $p$=0.334 for link density; $\beta_{Latitude}$=-0.001, $p$=0.354 for generality;
and $\beta_{Latitude}$=-0.001, $p$=0.334 for vulnerability). In lake food webs, link density,
generality, and vulnerability all increased more quickly towards the poles
($\beta_{Latitude:Lake}$=0.004, $p$=0.008; $\beta_{Latitude:Lake}$=0.005,
$p$=0.002; and $\beta_{Latitude:Lake}$=0.005, $p$=0.008, respectively) In
stream food webs generality increased more rapidly towards the poles 
($\beta_{Latitude}$=0.007, $p$=0.002) while link density and vulnerability did not vary with latitude.

In general, link density, generality, and vulnerability decreased as the
proportion of basal resources in a web increased (Fig.~\ref{B}). For
estuarine, lake, and stream food webs these decreases were more gradual towards the
poles ($\beta_{Latitude}$=-0.007, $p$=0.006 for link density;
$\beta_{Latitude}$=-0.009, $p$=0.002 for generality; and
$\beta_{Latitude}$=-0.007, $p$=0.006 for vulnerability).
In marine food webs there was very little effect of latitude on
the strength of scaling ($\beta_{Latitude:Marine}$=0.009, $p$=0.047; 
$\beta_{Latitude:Marine}$=0.011, $p$=0.028; 
and $\beta_{Latitude:Marine}$=0.009, $p$=0.047 respectively),
while in terrestrial food webs link density, generality, and vulnerability
decreased more gradually towards the 
equator ($\beta_{Latitude:Terrestrial}$=0.013, $p$=0.002; 
$\beta_{Latitude:Terrestrial}$=0.015, $p$=0.001; 
and $\beta_{Latitude:Terrestrial}$=0.013, $p$=0.002).

In contrast to the proportion of basal resources, link density, generality,
and vulnerability tended to increase with increasing proportions of
intermediate consumers (Fig.~\ref{I}). The best-fit models for scaling of link
density and vulnerability with the proportion of intermediate consumers did
not include any effect of latitude on scaling in any ecosystem type. Generality
increased more rapidly towards the equator in estuarine, lake, marine, and
stream food webs ($\beta_{Latitude}$=-0.006, $p$=0.009) and varied little with
latitude in terrestrial food webs ($\beta_{Latitude:Terrestrial}$=0.008,
$p$=0.053). In lake and stream food webs, generality increased more slowly
with the proporiton of intermediate consumers such that, at low proportions,
the effect of latitude could negate or reverse the increase.

As with the proportion of basal resources; link density, generality, and
vulnerability decreased as the proportion of top predators increased. For
estuarine, lake, and marine food webs scaling of link density, generality, and
vulnerability did not vary significantly with latitude
($\beta_{Latitude}$=-0.001, $p$=0.527 for link density;
$\beta_{Latitude}$=-0.001, $p$=0.526 for vulnerability; the best-fit model for
generality did not include any terms for latitude in any ecosystem type). In
stream and terrestrial food webs, the decrease in link density and
vulnerability was less sharp towards the poles, although this trend was
significant only in streams ($\beta_{Latitude:Stream}$=0.015,
$p$\textless0.001 and $\beta_{Latitude:Terrestrial}$=0.006, $p$=0.069 for link
density; $\beta_{Latitude:Stream}$=0.015, $p$\textless0.001 and
$\beta_{Latitude:Terrestrial}$=0.006, $p$=0.067 for vulnerability).
